Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-08-24 paper/main.tex
Clarify data origin

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI data, annotations, and results are available as Datalad \citep{datalad} datasets,
published to or linked from the
GIN repository \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
Unthresholded $Z$-maps of all contrasts can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

>>>>

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI data, annotations, and results are available as Datalad \citep{datalad} datasets,
published to or linked from the
GIN repository \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
The fMRI datasets for the movie and the audio-description were used in their original form, as published and available on the legacy OpenFMRI portal (\url{https://legacy.openfmri.org/dataset/ds000113}, \url{https://legacy.openfmri.org/dataset/ds000113c}, \url{https://legacy.openfmri.org/dataset/ds000113d}), as well as from \url{https://www.studyforrest.org} in the form of DataLad datasets.
The same data are available in a modified and merged form on OpenNeuro at \url{https://openneuro.org/datasets/ds000113}.
Unthresholded $Z$-maps of all contrasts can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
